Acceleration of plague outbreaks in the second pandemic

### 2020-07-05 ms_text.tex
improved (hopefully) last paragraph of Approach section

We can use independent estimates of the generation interval to estimate $\rzero$ (and hence the theoretical attack rate) for London epidemics under different transmission modes. By considering the additional (extreme) assumptions that \hypertarget{4assumptions}{} (1) the population was homogeneously mixed; (2) the population was initially 100\% susceptible; (3) there were no asymptomatic infections; and (4) all infected individuals died (\ie the CFP was 100\%), all of which increase the observed attack rate, we can calculate an upper bound on the total mortality we would expect to observe in an epidemic with a particular transmission mode.
%%
\david{I meant that if CFP$=1$ then all infected individuals get
  detected by mortality statistics, hence this would yield larger
  observed attack rate than if CFP$<1$.  Not sure this is
  sufficiently clear.}

>>>>

We can use independent estimates of the generation interval to estimate $\rzero$ (and hence the theoretical attack rate) for London epidemics under different transmission modes.  Given the limited information that we have, we consider the additional (extreme) assumptions that \hypertarget{4assumptions}{} (1) the population was homogeneously mixed; (2) the population was initially 100\% susceptible; (3) there were no asymptomatic infections; and (4) all infected individuals died (\ie the CFP was 100\%). All of these assumptions increase the observed attack rate (as detected from wills or deaths), so we can calculate an upper bound on the total mortality we would expect to observe in an epidemic with a particular transmission mode.
